Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Grilo and Thurik’s research [@Grilo2005b] is also often refered to about what determines entrepreneurship engagement levels throughout the European Union and the US.

Wennekers, Ulhaner and Thurik have looked more into variation across countries [@Wennekers2002]

Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.

Thus, what determines entrepreneurship at a country-level has been long searched already but although structural factors have been looked at extensively, much less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

>>>>

Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and at administrative complexities.

Actually, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors. Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ?????? 2010 VERSION MAIN BIB ?????. Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.

@@

In 2010, 
Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
